Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-10-16 manuscript.Rmd
cite measures

```{r other-measures-fig, cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:other-measures}Several measures for confirmation as an increase in firmness as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

>>>>

```{r other-measures-fig, cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:other-measures}Several measures for confirmation as an increase in firmness as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line). Measure taken from @sprengerBayesianPhilosophyScience2019, Table 1.3, p. 51."
